Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes

### 2019-04-13 GWLDCI.tex
Added corollary and reference in section 3

It will be important in the subsequent section to consider retriangulations.
\begin{dfn}
  If $W$ and $W'$ are weakly admissible Wilson loop diagrams on the same vertex set then $\tau(W)$ and $\tau(W')$  differ by a \emph{retriangulation} if there is a bijection $f$ between the maximal triangulated pieces of $\tau(W)$ and the maximal triangulated pieces of $\tau(W')$ such that for any triangulated piece $t$ of $\tau(W)$ the vertex sets of $t$ and $f(t)$ are the same.
\end{dfn}
More casually this definition says that the triangulated pieces of $\tau(W)$ and $\tau(W')$ are the same (so far as their vertex sets are concerned) but that some or all of the triangulated pieces may be differently triangulated while the region being triangulated by each piece (which is defined by the vertex set) remains unchanged.

@@

@@

\begin{proof}
  Let $W$ and $X$ be two equivalent Wilson loop diagrams.  From Lemma~\ref{lem triang to exact} along with the definitions of $\sim$ and retriangulation, we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.

@@

>>>>

It will be important in the subsequent section to consider retriangulations.
\begin{dfn} \label{retriangulation}
  If $W = (\cP, [n])$ and $W' = (\cP', [n])$ are weakly admissible Wilson loop diagrams, then $\tau(W)$ and $\tau(W')$  differ by a \emph{retriangulation} if there is a bijection $f$ between the maximal triangulated pieces of $\tau(W)$ and the maximal triangulated pieces of $\tau(W')$ such that for any triangulated piece $t$ of $\tau(W)$ the vertex sets of $t$ and $f(t)$ are the same.
\end{dfn}
More casually this definition says that the maximal triangulated pieces of $\tau(W)$ and $\tau(W')$ are the same (so far as their vertex sets are concerned) but that some or all of the triangulated pieces may be differently triangulated while the region being triangulated by each piece (which is defined by the vertex set) remains unchanged. Note that these maximal triangulations correspond to non-crossing partitions of the Wilson loop diagram, in the sense discussed in \cite{positroids13}.

@@

Finally, we may express equivalent Wilson loop diagrams in terms of retriangulations.

\begin{cor}\label{equialentretriangulation}
Two Wilson loop diagrams, $W$ and $W'$ are equivalent if and only if $\tau(W)$ and $\tau(W')$ differ by retriangulations.
\end{cor}

\begin{proof}
This follows from the definition of equivalent Wilson loop diagrams, Definition \ref{equivdfn}, the definition of retriangulations, Definition \ref{retriangulation}, and Lemma\ref{lem triang to exact}.
\end{proof}

@@

\begin{proof}
  Let $W$ and $X$ be two equivalent Wilson loop diagrams.  From Corrolary \ref{equialentretriangulation} we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.

@@

\bibitem{positroids13}
Federico Ardila, Felipe Rinc{\'{o}}n, and Lauren Williams.
\newblock Positroids and non-crossing partitions.
\newblock {\em Transactions of the American Mathematical Society}, 2015.
\newblock arXiv:1308.2698v2.
